Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline

### 2017-08-30 Ben_Manuscripts/Paper1/Outline.tex
outlining phase transition section

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{geometry}
\geometry{legalpaper, margin=1in}
\usepackage{amsmath} % or simply amstext
\newcommand{\angstrom}{\textup{\AA}}
\title{Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline}
\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts} 
\begin{document}
  \bibliographystyle{ieeetr}
  \graphicspath{{./figures/}}
  \maketitle
  \section*{Introduction}

@@

  While RO and NF have seen many advances in the past few decades, they 
  are far from perfect separation technologies.
  \begin{itemize}
    \textit{RO membranes}
    \item \textbf{Inconsistent performance} : Current state-of-the-art RO membranes are unstructured with
    tortuous and polydisperse diffusion pathways which leads to 
    inconsistent performance \cite{song_nano_2011}
    \item \textbf{High energy requirements} : Necessarily high feed pressures 
    drive up energy requirements which strains developing regions and
    contributes strongly to CO\textsubscript{2} emissions. \cite{mcginnis_global_2008}
    \item \textbf{Separation based on differences in solubility and diffusivity:
    Moreover, designing RO membranes to achieve targeted separations of 
    specific solutes is nearly impossible because various solutes dissolve
    into and diffuse through the polymer matrix at different rates. \cite{wijmans_solution-diffusion_1995}
    \item At best, one can exploit these differences to create a functional
    selective barrier.
    \textit{NF membranes}
    \item NF was introduced as an intermediate between RO and ultrafiltration,
    having the ability to separate organic matter and salts on the order of 
    one nanometer in size.
    \item Larger and well-defined pores drive down energy requirements while
    still affording separation of solutes as small as ions to some degree \cite{van_der_bruggen_review_2003}
    \item NF is often used as a precursor to reverse osmosis
    \item Unfortunately, NF membranes, like RO, are produced with a pore size 
    distribution which limits their ability to perform precise separations \cite{bowen_modelling_2002}
  \end{itemize}

@@

  \begin{figure}[H]
	\centering
	\includegraphics[width=0.75\linewidth]{build.PNG} %BJC: put an xyz axis with the unit cell
	\caption{(a) A single monomer was parameterized and annealed to produce a low energy
		configuration. (b) Monomers are rotated and assembled into layers with 
		hydrophlic centers. (c) Twenty layers are stacked on top of each other to create
		a pore. (d) Pores are duplicated and placed in a monoclinic unit cell}\label{fig:python}
  \end{figure}

@@

  \begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{sandwiched.png}
		\caption{}\label{fig:sandwiched}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{PD.png}
		\caption{}\label{fig:pd}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Tshaped.png}
		\caption{}\label{fig:tshaped}
	\end{subfigure}
	\vskip\baselineskip
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{sandwichedlayers.png}
		\caption{}\label{fig:sandwichedlayers}
	\end{subfigure}
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{offsetlayers.png}
		\caption{}\label{fig:offsetlayers}
	\end{subfigure}
	\caption{(a) Sandwiched benzene dimers stack 3.8 \angstrom apart. (b) Parallel-Displaced benzene dimers stack
	3.4 \angstrom vertically and 1.6 \angstrom horizontally apart. (c) T-shaped benzene dimers stack 5.0 \angstrom apart. 
	(d) Two monomer layers stacked in the sandwiched configuration (e) Two monomer layers stacked in the parallel-displaced
	configuration }\label{fig:stacking}
  \end{figure}

@@

  \begin{table}[H]
  \centering
  \begin{tabular}{ccc}
  \toprule
  		   & \multicolumn{2}{c}{Starting Configuration} \\
  \hline
  Monomers per layer & Sandwiched & Parallel Displaced \\
  \midrule
  4 & $3.71 \pm 0.04$ & $3.82 \pm 0.03$ \\
  5 & $4.20 \pm 0.04$ & $4.23 \pm 0.04$ \\
  6 & $4.83 \pm 0.03$ & $4.85 \pm 0.02$ \\
  7 & $4.73 \pm 0.03$ & $4.84 \pm 0.03$ \\
  8 & $5.08 \pm 0.04$ & $5.46 \pm 0.03$ \\
  \bottomrule
  \end{tabular}
  \caption{The pore spacing of the model increases as number of monomers
  in each layer increases. The pore spacing of a system starting in the 
  sandwiched configuration is systematically lower than that started in an 
  offset configuration. Systems built with 5 monomers per layer in a parallel
  displaced configuration result in a pore spacing closest to experimental
  data}\label{table:p2p} 
  \end{table}

@@

  \begin{figure}[H]
	\centering
	\begin{subfigure}{0.31\textwidth}
		\centering
		\hspace{-0.9cm}
		\includegraphics[width=\textwidth]{sandwich_rzplot.png}
		\caption{}\label{fig:sandwich_rzplot}
	\end{subfigure}
	\begin{subfigure}{0.31\textwidth}
		\centering
		\hspace{-0.9cm}
		\includegraphics[width=\textwidth]{offset_rzplot.png}
		\caption{}\label{fig:offsetrzplot}
	\end{subfigure}
	\begin{subfigure}{0.31\textwidth}
		\centering
		\hspace{-0.9cm}
		\includegraphics[width=\textwidth]{disorder_rzplot.png}
		\caption{}\label{fig:disorder_rzplot.png}
	\end{subfigure}
	\caption{(a) All major features except R-helix are present in
	XRD patterns resulting from an equilibrated sandwiched configuration 
	in Basin A. R-pi intersescts R-alkanes. R-helix faded during equilbration.
	(b) All major features execpt R-spots are present in XRD patterns 
	resulting from an equilibrated parallel displaced configuration in Basin A.
	R-helix exists faintly in the expected location. (c) R-pores and R-alkanes
	are the only major features present in XRD patterns resulting from an 
	equilibrated disordered phase}\label{fig:XRDsim}
  \end{figure}

@@

  Basin A and Basin B are two configurationally metastable basins.
  \begin{itemize}
  	\item We hesitate to classify the basins as separate phases.
	\item We hypothesize that Basin B is present at higher temperatures.
	\item This is evidenced by a simulation of a system in Basin A whose temperature
	was linearly ramped from 280K to 340K over 100 ns.
	\item Visually, there is a distinct change in pore structure from one
	characteristic of Basin A (Figure~\ref{fig:280K_pore}) to one characteristic of 
	Basin B (Figure~\ref{fig:340K_pore}).
	\item To quantify our observation, we chose three easily measurable order 
	parameters: the distance between pores, the membrane thickness and the
	ratio of pore radius to the uncertainty in pore radius.
	\item The pore radius is divided by its uncertainty in order to understand
	the degree to which monomers obstruct the pore region.
	\item Referring back to our temperature ramped system, the slope of all 
	order parameters change around 315K - 325K 
	(\Cref{fig:p2p_tramp,fig:thickness_tramp,fig:order_tramp}) indicating the 
	possibility of an abrupt change in system ordering.
	\item To prove that the basins are in fact two different phases, we must 
	observe evidence of a first order phase transition, which would be marked 
	by a discontinuity in an order parameter as a function of temperature.
	\item Our 100 ns temperature ramp may have been too fast causing the system
	to suffer from hysteresis.
	%BJC: should this go in methods?
	\item To mitigate hysteresis, we performed a slow, stepwise temperature ramp.
	\item Starting from a sandwiched structure equilibrated at 280K, the system
	temperature was raised to 300K and allowed to equilibrate for 200 ns.
	\item At the end of 200 ns, the temperature was raised 5K and equilibrated 
	again for 200 ns.
	\item We continued raising the temperature by 5K and equilibrating for 200 ns
	until the system was equilibrated for 200 ns at 320K.
	\item In all cases, we observed smooth changes in order parameters as temperature
	was increased implying that we can not yet claim the existence of two phases 
	(Figure~\ref{fig:phase_transition}).
	\item I have this run out to about 335K right now. I have to see if there is anything
	noteworthy to report

@@

  \begin{table}[H]
  \centering
  \begin{tabular}{ccc}
  \toprule
  \multicolumn{3}{c}{Calculated Ionic Conductivity \si{\siemens\per\meter}} \\
  \hline
  Method & Basin A & Basin B \\
  \midrule
  Nernst Einstein & \num{1.23e-4} (0.01) & \num{1.76e-4} (0.02) \\
  Collective Diffusion & \num{1.40e-4} (0.32) & \num{4.6e-4}(2.4) \\
  Experiment & \num{1.33e-5} (0.10) & -- \\
  \bottomrule
  \end{tabular}
  \caption{Calculated ionic conductivity using Nernst-Einsten and Collective Diffusion 
  agree within error. Both methods give calculated values of ionic conductivity which
  are an order of magnitude higher than experimental values~\label{table:conductivity}}.
  \end{table}

@@

  We applied the crosslinking algorithm to the equilibrated sandwiched structure in 
  Basin A.
  \begin{itemize}  %BJC: working on the following. The following is what I expect
  	\item There is an even distribution of crosslinks between same monomer tails, 
	between monomers in the same pore and between monomers in different pores 
	including periodic boundaries.
	\item The distance between pores shrinks by 1 \angstrom after the system is 
	crosslinked
	\item Major features are still present in the X-ray diffraction
	\item The ionic conductivity is higher/lower in the crosslinked system
  \end{itemize}
  %BJC: THe following figure will be replaced with one representative of the new
  % data I am  collecting above.
  \begin{figure}[H]
	\centering
	\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{p2p_diagram.PNG}
		\caption{}\label{fig:p2p_diagram}
	\end{subfigure}
		\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{no_xlink_p2p.png}
		\caption{}\label{fig:no_xlink_p2p}
	\end{subfigure}
		\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{xlink_p2p.png}
		\caption{}\label{fig:xlink_p2p}
	\end{subfigure}
	\caption{(a) The legends of the plots in (b) and (c) refer to the numbers shown.
	Each numbered circle represents a pore. Distances are measured along each of the 
	lines shown in addition to the distance from pore 1 to pore 4. (b) The positions
	of individual pores fluctuate in an uncrosslinked system. (c) The positions of
	individual pores in the crosslinked system are stable relative to the uncrosslinked
	system}\label{fig:xlink}
  \end{figure}

>>>>

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\title{Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline}
\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts} 
\begin{document}
  \bibliographystyle{ieeetr}
  \graphicspath{{./figures/}}
  \maketitle
  \section*{Introduction}

@@

  While RO and NF have seen many advances in the past few decades, they 
  are far from perfect separation technologies.
  \begin{itemize}
    \item \textit{RO membranes}
    \item \textbf{Inconsistent performance} : Current state-of-the-art RO membranes are unstructured with
    tortuous and polydisperse diffusion pathways which leads to 
    inconsistent performance \cite{song_nano_2011}
    \item \textbf{High energy requirements} : Necessarily high feed pressures 
    drive up energy requirements which strains developing regions and
    contributes strongly to CO\textsubscript{2} emissions. \cite{mcginnis_global_2008}
    \item \textbf{Separation based on differences in solubility and diffusivity}:
    Moreover, designing RO membranes to achieve targeted separations of 
    specific solutes is nearly impossible because various solutes dissolve
    into and diffuse through the polymer matrix at different rates. \cite{wijmans_solution-diffusion_1995}
    \item At best, one can exploit these differences to create a functional
    selective barrier.
    \item \textit{NF membranes}
    \item NF was introduced as an intermediate between RO and ultrafiltration,
    having the ability to separate organic matter and salts on the order of 
    one nanometer in size.
    \item Larger and well-defined pores drive down energy requirements while
    still affording separation of solutes as small as ions to some degree \cite{van_der_bruggen_review_2003}
    \item NF is often used as a precursor to reverse osmosis
    \item Unfortunately, NF membranes, like RO, are produced with a pore size 
    distribution which limits their ability to perform precise separations \cite{bowen_modelling_2002}
  \end{itemize}

@@

  \begin{figure}[h]
	\centering
	\includegraphics[width=0.75\linewidth]{build.PNG} %BJC: put an xyz axis with the unit cell
	\caption{(a) A single monomer was parameterized and annealed to produce a low energy
		configuration. (b) Monomers are rotated and assembled into layers with 
		hydrophlic centers. (c) Twenty layers are stacked on top of each other to create
		a pore. (d) Pores are duplicated and placed in a monoclinic unit cell}\label{fig:python}
  \end{figure}

@@

  \begin{figure}[h]
	\centering
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{sandwiched.png}
		\caption{}\label{fig:sandwiched}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{PD.png}
		\caption{}\label{fig:pd}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Tshaped.png}
		\caption{}\label{fig:tshaped}
	\end{subfigure}
	\vskip\baselineskip
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{sandwichedlayers.png}
		\caption{}\label{fig:sandwichedlayers}
	\end{subfigure}
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{offsetlayers.png}
		\caption{}\label{fig:offsetlayers}
	\end{subfigure}
	\caption{(a) Sandwiched benzene dimers stack 3.8 \angstrom apart. (b) Parallel-Displaced benzene dimers stack
	3.4 \angstrom vertically and 1.6 \angstrom horizontally apart. (c) T-shaped benzene dimers stack 5.0 \angstrom apart. 
	(d) Two monomer layers stacked in the sandwiched configuration (e) Two monomer layers stacked in the parallel-displaced
	configuration }\label{fig:stacking}
  \end{figure}

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{ccc}
  \toprule
  		   & \multicolumn{2}{c}{Starting Configuration} \\
  \hline
  Monomers per layer & Sandwiched & Parallel Displaced \\
  \midrule
  4 & $3.71 \pm 0.04$ & $3.82 \pm 0.03$ \\
  5 & $4.20 \pm 0.04$ & $4.23 \pm 0.04$ \\
  6 & $4.83 \pm 0.03$ & $4.85 \pm 0.02$ \\
  7 & $4.73 \pm 0.03$ & $4.84 \pm 0.03$ \\
  8 & $5.08 \pm 0.04$ & $5.46 \pm 0.03$ \\
  \bottomrule
  \end{tabular}
  \caption{The pore spacing of the model increases as number of monomers
  in each layer increases. The pore spacing of a system starting in the 
  sandwiched configuration is systematically lower than that started in an 
  offset configuration. Systems built with 5 monomers per layer in a parallel
  displaced configuration result in a pore spacing closest to experimental
  data}\label{table:p2p} 
  \end{table}

@@

  \begin{figure}[h]
	\centering
	\begin{subfigure}{0.31\textwidth}
		\centering
		\hspace{-0.9cm}
		\includegraphics[width=\textwidth]{sandwich_rzplot.png}
		\caption{}\label{fig:sandwich_rzplot}
	\end{subfigure}
	\begin{subfigure}{0.31\textwidth}
		\centering
		\hspace{-0.9cm}
		\includegraphics[width=\textwidth]{offset_rzplot.png}
		\caption{}\label{fig:offsetrzplot}
	\end{subfigure}
	\begin{subfigure}{0.31\textwidth}
		\centering
		\hspace{-0.9cm}
		\includegraphics[width=\textwidth]{disorder_rzplot.png}
		\caption{}\label{fig:disorder_rzplot.png}
	\end{subfigure}
	\caption{(a) All major features except R-helix are present in
	XRD patterns resulting from an equilibrated sandwiched configuration 
	in Basin A. R-pi intersescts R-alkanes. R-helix faded during equilbration.
	(b) All major features execpt R-spots are present in XRD patterns 
	resulting from an equilibrated parallel displaced configuration in Basin A.
	R-helix exists faintly in the expected location. (c) R-pores and R-alkanes
	are the only major features present in XRD patterns resulting from an 
	equilibrated disordered phase}\label{fig:XRDsim}
  \end{figure}

@@

  Basin A and Basin B are two configurationally metastable basins.
  \begin{itemize}
  	\item We hesitate to classify the basins as separate phases.
	\item We hypothesize that Basin B is present at higher temperatures.
	\item This is evidenced by a simulation of a system in Basin A whose temperature
	was linearly ramped from 280K to 340K over 100 ns.
	\item Visually, there is a distinct change in pore structure from one
	characteristic of Basin A (Figure~\ref{fig:280K_pore}) to one characteristic of 
	Basin B (Figure~\ref{fig:340K_pore}).
	\item To quantify our observation, we chose three easily measurable order 
	parameters: the distance between pores, the membrane thickness and the
	ratio of pore radius to the uncertainty in pore radius.
	\item The pore radius is divided by its uncertainty in order to understand
	the degree to which monomers obstruct the pore region.
	\item Referring back to our temperature ramped system, the slope of all 
	order parameters change around 315K - 325K 
	(\Cref{fig:p2p_tramp,fig:thickness_tramp,fig:order_tramp}) indicating the 
	possibility of an abrupt change in system ordering.
	\item To prove that the basins are in fact two different phases, we must 
	observe evidence of a first order phase transition, which would be marked 
	by a discontinuity in an order parameter as a function of temperature.
	\item Our 100 ns temperature ramp may have been too fast causing the system
	to suffer from hysteresis.
	%BJC: should this go in methods?
	\item To mitigate hysteresis, we performed a slow, stepwise temperature ramp.
	\item Starting from a sandwiched structure equilibrated at 280K, the system
	temperature was raised to 300K and allowed to equilibrate for 200 ns.
	\item At the end of 200 ns, the temperature was raised 5K and equilibrated 
	again for 200 ns.
	\item We continued raising the temperature by 5K and equilibrating for 200 ns
	until the system was equilibrated for 200 ns at 320K.
	\item In all cases, we observed smooth changes in order parameters as temperature
	was increased implying that we can not yet claim the existence of two phases 
	(Figure~\ref{fig:phase_transition}).
	\item I have this run out to about 335K right now. I have to see if there is anything
	noteworthy to report	
  \end{itemize}

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{ccc}
  \toprule
  \multicolumn{3}{c}{Calculated Ionic Conductivity \si{\siemens\per\meter}} \\
  \hline
  Method & Basin A & Basin B \\
  \midrule
  Nernst Einstein & \num{1.23e-4} (0.01) & \num{1.76e-4} (0.02) \\
  Collective Diffusion & \num{1.40e-4} (0.32) & \num{4.6e-4}(2.4) \\
  Experiment & \num{1.33e-5} (0.10) & -- \\
  \bottomrule
  \end{tabular}
  \caption{Calculated ionic conductivity using Nernst-Einsten and Collective Diffusion 
  agree within error. Both methods give calculated values of ionic conductivity which
  are an order of magnitude higher than experimental values~\label{table:conductivity}}.
  \end{table}

@@

  We applied the crosslinking algorithm to the equilibrated sandwiched structure in 
  Basin A.
  \begin{itemize}  %BJC: working on the following. The following is what I expect
  	\item There is an even distribution of crosslinks between same monomer tails, 
	between monomers in the same pore and between monomers in different pores 
	including periodic boundaries.
	\item The distance between pores shrinks by 1 \angstrom after the system is 
	crosslinked
	\item Major features are still present in the X-ray diffraction
	\item The ionic conductivity is higher/lower in the crosslinked system
  \end{itemize}
  %BJC: THe following figure will be replaced with one representative of the new
  % data I am  collecting above.
  \begin{figure}[h]
	\centering
	\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{p2p_diagram.PNG}
		\caption{}\label{fig:p2p_diagram}
	\end{subfigure}
		\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{no_xlink_p2p.png}
		\caption{}\label{fig:no_xlink_p2p}
	\end{subfigure}
		\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{xlink_p2p.png}
		\caption{}\label{fig:xlink_p2p}
	\end{subfigure}
	\caption{(a) The legends of the plots in (b) and (c) refer to the numbers shown.
	Each numbered circle represents a pore. Distances are measured along each of the 
	lines shown in addition to the distance from pore 1 to pore 4. (b) The positions
	of individual pores fluctuate in an uncrosslinked system. (c) The positions of
	individual pores in the crosslinked system are stable relative to the uncrosslinked
	system}\label{fig:xlink}
  \end{figure}
\end{document}
